Visualizations for the manuscript

### 2022-03-15 metanalysis_visualization/manuscript_Figures.Rmd
Adding mean age calculation

@@

table1 <- rbind( sex_table1_all, dg_table1_all )

@@

## Boostrap vizualisation
```{r}
# Recovering
coefficient_slope_calculation <- function(df, ...) {
  ts_linear_percent <- lm(percentage ~ period * time, df)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("periodduring_pandemic:time"))
}

@@

@@

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf, y = +Inf, hjust=0, vjust=1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```

>>>>

```{r Extracting age information}

age_table1_all <- table1_all %>% 
  filter(name == "Age" | (name == "Total" & Category == "Sex")) %>% 
  select(name, siteid, before_pandemic, during_pandemic) %>% 
  pivot_longer(cols = c(before_pandemic, during_pandemic), 
               names_to = "period",
               values_to = "values") %>% 
  pivot_wider(names_from = name, 
              values_from = values, 
              id_cols = c(siteid, period)) %>% 
  mutate(mean_age = as.numeric(sub("\\s\\(.*", "", x = Age, perl = TRUE)),
         sd_age = as.numeric(str_extract(pattern = "(?<=\\(sd:\\s)[0-9]{1,2}\\.[0-9]{1,2}(?=\\))", 
                                         string = Age)),
         Total = as.numeric(sub("\\s\\(.*", "", x = Total, perl = TRUE))
  ) %>% 
  group_by(period) %>% 
  summarise(mean_age = round(sum(Total * mean_age) / sum(Total), 2), 
            sd_age = round(sum(Total * sd_age) / sum(Total), 2)) %>% 
  mutate(Age = paste0(as.character(mean_age), " (sd: ", as.character(sd_age), ")")) %>% 
  select(period, Age) %>% 
  pivot_wider(names_from = period, values_from = Age) %>% 
  mutate(Category = "Age", 
         name = "mean (sd)") %>% 
  select(Category, name, before_pandemic, during_pandemic) %>% 
  rename(before_pandemic_count = before_pandemic, 
         during_pandemic_count = during_pandemic)
```

@@

table1 <- rbind( sex_table1_all, age_table1_all, dg_table1_all )

@@

```{r}
# Recovering
coefficient_slope_calculation <- function(df, ...) {
  ts_linear_percent <- lm(percentage ~ period * time, df)
  linear_model <- broom::tidy(ts_linear_percent) %>%
    filter(term %in% c("periodduring_pandemic:time"))
}

@@

### Primary analysis

@@

ggplot(bootstrapped_fitted_all, aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("siteid", scales = "free_y") +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_all,
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_all[quantile_bootstrapped_fitted_all$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patient_count_psy_period_psy_all,
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(title = "Interrupted Time Series Analysis: Percentage of patients with psychiatric conditions",
       subtitle = "Parametric bootstrap estimation: (1000 iterations)",
       x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8), 
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 12, face = "italic")) 
ggsave("boostrapped_all.png", height = 20, width = 32, units = "cm")
```
